DraftOne

### 2016-06-23 writing/JSSDraft/JSSDraft.Rmd
Figure out bibliography for JSS draft

---
author:
  - name: Sarah Koehler
    affiliation: Colorado State University
    address: >
      Lake Street
      Fort Collins, CO
    email: sakoehler7@gmail.com
  - name: G. Brooke Anderson
    affiliation: Colorado State University
    address: >
      Lake Street
      Fort Collins, CO
    email: brooke.anderson@colostate.edu
title:
  formatted: "\\pkg{eesim}: A Package to Simulate Environmental Epidemiology Time Series for Simulation Studies and Power Analyses"
  # If you use tex in the formatted title, also supply version without
  plain:     "eesim: A Package to Simulate Environmental Epidemiology Time Series for Simulation Studies and Power Analyses"
  # For running headers, if needed
  short:     "\\pkg{eesim}: Simulations for Environmental Epidemiology"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [environmental epidemiology, simulation studies, power analysis, air pollution]
  plain:     [environmental epidemiology, simulation studies, power analysis, air pollution]
preamble: >
  \usepackage{amsmath}
output: rticles::jss_article
---

# Purpose of package

@@

# Package functionality

@@

>>>>

---
author:
  - name: Sarah Koehler
    affiliation: Colorado State University
    address: >
      Lake Street
      Fort Collins, CO
    email: sakoehler7@gmail.com
  - name: G. Brooke Anderson
    affiliation: Colorado State University
    address: >
      Lake Street
      Fort Collins, CO
    email: brooke.anderson@colostate.edu
title:
  formatted: "\\pkg{eesim}: An R Package to Simulate Environmental Epidemiology Time Series for Simulation Studies and Power Analyses"
  # If you use tex in the formatted title, also supply version without
  plain:     "eesim: An R Package to Simulate Environmental Epidemiology Time Series for Simulation Studies and Power Analyses"
  # For running headers, if needed
  short:     "\\pkg{eesim}: Simulations for Environmental Epidemiology"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [R, environmental epidemiology, simulation studies, power analysis, air pollution]
  plain:     [R, environmental epidemiology, simulation studies, power analysis, air pollution]
preamble: >
  \usepackage{amsmath}
output:
  rticles::jss_article:
    citation_package: natbib
bibliography: mybibfile.bib
---

# Introduction

@@

# Basic overview of package

# Implementing the package

@@

Example citation [@Dirac1953888].

# Discussion

# Acknowledgments

# References
